---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# similiars

<!-- badges: start -->
<!-- badges: end -->

The goal of similars is to match strings to the most similar string in another vector.

## Installation

You can install the released version of `similiars` with:

``` r
remotes::install_github("davidsjoberg/similiars")
```

### `find_most_similar_string`

The main function included is `find_most_similar_string` which returns a vector of the same length as the vector to be matched against another.

```{r example2}
library(similiars)

x <- c("aple", "anana", "pech")
find_most_similar_string(x, stringr::fruit)

```

### `find_string_distance`

The other function is `find_string_distance`. It returns a list of dataframes for each word and how similar each string is to all matched strings. If you are not sure if there is a good match to be found it is good practise to use this function before using `find_most_similar_string`.

```{r example}
find_string_distance(c("aple", "abna"),
                     c("banana", "apple", "pineapple"))
```

### `case_when_skeleton`

If you want manual control over which should be replaced you can create a `case_when` code chunk to use in your script.

```{r example3}
# Misspelled vector
supr_heros   <- c("Btman", "Supergrl", "Tor", "Capitan 'Murica")
# Corrected vector
super_heroes <- find_most_similar_string(supr_heros, superheroes)

# Make case_when skeleton to replace
case_when_skeleton(supr_heros, super_heroes)
```

***

If you find anything you want to improve, submit an issue :)