---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# similiars

<!-- badges: start -->
<!-- badges: end -->

The goal of similiars is to match strings to the most similiar string in another vector.

## Installation

You can install the released version of similiars with:

``` r
remotes::install_github("davidsjoberg/similiars")
```

### `find_most_similiar_string`

The main function included is `find_most_similiar_string` which returns a vector of the same length as the vector to be matched against another.

```{r example2}
library(similiars)
library(stringr)

x <- c("aple", "anana", "pech")
find_most_similiar_string(x, fruit)

```

### `find_string_distance`

The other function is `find_string_distance`. It returns a list of dataframes for each word and how similiar each string is to all matched strings. If you are not sure if there is a good match to be found it is good practise to use this function before using `find_most_similiar_string`.

```{r example}
library(similiars)
find_string_distance(c("aple", "abna"),
                     c("banana", "apple", "pineapple"))
```

***

If you find anything you want to improve, submit an issue :)